Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-07-18 article.tex
typo
some changes in appendix C

The main idea of principal component analysis (PCA) is to reduce the
dimensionality of a dataset whose variables are interrelated
\citep{jolliffe2005principal}. It consists in finding a new ordered set of
uncorrelated variables, called the principal components, where the most
principal components, i.e. the first variables, hold most of the data variation, also denoted as
variance, scattered in all the original variables.

Figure~\ref{fig:pca} shows the explained variance by compoments and gives a hint about the number of uncorrelated variables required to
explain all the variation in the original data.

@@

Obvioulsy, Figure~\ref{fig:pca} shows that for both approaches only 800
components are required to explain the (majority of) network structures.
Therefore, the value of the parameter $M$ is immediat and should be obviously
set to $800$, or equivalently to $0.8p$. \\

@@

\begin{table}[h]
\caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
\label{tab:results_appendix}
\centering
\small
\begin{tabular}{| l|c|c|c|} \hline
Methods & Execution time & Scalability & Memory requirements \\ \hline
Partial correlation & & & \\ 
GTE  & & & \\
GENIE3 & & & \\ \hline
\end{tabular}
\end{table}

>>>>

The main idea of principal component analysis (PCA) is to reduce the
dimensionality of a dataset whose variables are interrelated
\citep{jolliffe2005principal}. It consists in finding a new set of
uncorrelated variables, denoted as principal components, where the most
principal components, assuming an order between the components, hold most of the variance of the data scattered in all the original variables.

Figure~\ref{fig:pca} shows the explained variance (ratio) by compoments and gives a hint about the number of uncorrelated variables required to
explain all - or, at least, the majority of -  the variation in the original data.

@@

Obvioulsy, Figure~\ref{fig:pca} shows that for both approaches only 800
components are required to explain the (majority of) network structures.
Therefore, the value of the parameter $M$ is immediat and should be clearly
set to $800$, or equivalently to $0.8p$. \\

@@

To perform experiments, we used a Macbook Pro (2014) with a ram memory 16Go 1600 MHz DDR3 and a processor 2.3GHz Intel Core i7.

In order to compare the execution time with other methods, it takes about xx and xx hours to compute respectively GTE and GENIE3. However, GENIE3 is highly parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.

\begin{table}[h]
\caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
\label{tab:results_appendix}
\centering
\small
\begin{tabular}{| l|c|c|} \hline
Methods & Execution time  & Memory requirements \\ \hline
PC & & $\sim$5Go\\
Averaging & & \\
Full Method & & \\ \hline
\end{tabular}
\end{table}
